Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-09-25 paper/appendix.tex
supp
pushing things in appendix

@@

>>>>

For B2B, feature importance is assessed as follows:

\begin{algorithm}[H]
    %\SetAlgoLined
    \KwIn{$X_{train} \in \mathbb{R}^{n \times d_x}$, $X_{test} \in
\mathbb{R}^{n' \times d_x}$, $Y_{train} \in \mathbb{R}^{n\times d_y}$, $Y_{test}
\in \mathbb{R}^{n'\times d_y}$, } \KwOut{estimate of prediction improvement
$\Delta{R} \in \mathbb{D}^{d_x}$.} $H, G = \text{B2B}(X_{train}, Y_{train})$\;
$R_{full} = \text{corr}(X_{test} H, Y_{test} G)$\;

    \For{$i = 1, \ldots, d_x$}{ $K = Id$\; $K[i] \leftarrow 0$\; $H_k =
\text{LinearRegression}(X_{train} K, Y_{train} G_i)$\; $R_{k} =
\text{corr}(X_{test} H_k, Y_{test} G_i)$\; $\Delta R_i = R_{full} - R_{k}$\; }
\Return{$\Delta R$} \caption{B2B feature importance.} \label{algorithm:b2b_fi}
\end{algorithm}

@@

\section{Additional Figures}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_supp.pdf}
  \caption{}
  \label{fig:meg_supp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/AUC_R.png}
  \caption{Synthetic experiments. Distribution (over conditions) of differences in AUC (left) and Feature Importance $\Delta R$ (right) metrics between our method and the baselines. Mass under the dashed line corresponds to B2B outperforming the baseline. \label{fig:auc_plots}}
\end{figure}
